---
title: "R Markdown Presentation & Plotly"
author: "Sujitha P"
date: "December 26, 2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown Presentation & Plotly

Create a web page presentation using R Markdown that features a plot created with Plotly. Host your webpage on either GitHub Pages, RPubs, or NeoCities. Your webpage must contain the date that you created the document, and it must contain a plot created with Plotly. We would love to see you show off your creativity!

The Interactive Plots presented in this Assignment are as follows -

1. A Heatmap depicting the Daily Ozone Levels in New York over a period of 5 months (May to September 1973).
2. A Time-Series chart of the Population of the United States (in millions) for the period 1790-1970.

## Data Processing for Plot 1 : Heatmap R Code{.smaller}

```{r results='hide'}
library(datasets);library(plotly);library(reshape2)
data("airquality") ## Load the airquality dataset
airquality$Month=as.factor(airquality$Month) ## Convert Month to factor
ozone_daily=airquality[,c(1,5,6)] ## Extract Ozone, Month and Day columns
## Convert Long format to Wide for input to Heatmap
ozone_daily=dcast(ozone_daily,Day~Month,value.var = "Ozone") 
ozone_daily=as.matrix(ozone_daily[,-1]) ## Convert to Matrix
colnames(ozone_daily)=c("May","June","July","August","September")
## Plotly command
plot_ly(z=ozone_daily,colorscale="Hot",x=colnames(ozone_daily),type="heatmap",colorbar = list(title = "Ozone Levels (parts per billion)"))%>%layout(title = "Daily Ozone Levels in New York, May to September 1973", xaxis = list(title = "Month"),yaxis = list(title = "Day"))
```

## Plotly - Interactive Plot 1: Heatmap

```{r echo=FALSE}
library(datasets);library(plotly);library(reshape2)
data("airquality") ## Load the airquality dataset
airquality$Month=as.factor(airquality$Month) ## Convert Month to factor
ozone_daily=airquality[,c(1,5,6)] ## Extract Ozone, Month and Day columns
## Convert Long format to Wide for input to Heatmap
ozone_daily=dcast(ozone_daily,Day~Month,value.var = "Ozone") 
ozone_daily=as.matrix(ozone_daily[,-1]) ## Convert to Matrix
colnames(ozone_daily)=c("May","June","July","August","September")
## Plotly command
plot_ly(z=ozone_daily,colorscale="Hot",x=colnames(ozone_daily),type="heatmap",colorbar = list(title = "Ozone Levels (parts per billion)"))%>%layout(title = "Daily Ozone Levels in New York, May to September 1973", xaxis = list(title = "Month"),yaxis = list(title = "Day"))
```

## Plot 2 : Time-Series Chart R Code{.smaller}

```{r }
library(datasets)
library(plotly)
data(uspop) ## Load the data set that gives the population of the United States 
## (in millions) as recorded by the decennial census for the period 1790-1970.
## Plotly Command
plot_ly(x=~time(uspop),y=~uspop,type="scatter",mode="lines") %>% layout(title = "U.S. Population in millions for the period 1790-1970", xaxis = list(title = "Year"),yaxis = list(title = "U.S. Population (millions)"))
```

## Plotly - Interactive Plot 2: Time-Series Chart

```{r echo=FALSE}
library(datasets)
library(plotly)
data(uspop) ## Load the data set that gives the population of the United States in millions for the period 1790-1970
## Plotly Command
plot_ly(x=~time(uspop),y=~uspop,type="scatter",mode="lines") %>% layout(title = "U.S. Population in millions for the period 1790-1970", xaxis = list(title = "Year"),yaxis = list(title = "U.S. Population (millions)"))
```
